\section{Preliminaries}
\subsection{Threshold FHE}
\cite{jain2017threshold} defines threshold FHE encryption. For the sake of completeness, we will define it here.

\begin{definition}[TFHE]
	Let $P = \set{P_1, ..., P_N}$	 be a set of $N$ parties and $\mathbb{S}$ be a class of
	access structures on $P$. A TFHE scheme for $\mathbb{S}$ is a tuple of PPT algorithms
	$$
		(\TFHESetup, \TFHEEncrypt, \TFHEEval, \TFHEPartDec, \TFHEFinDec)
	$$ such that the following specifications are met

	\begin{itemize}
		\item $(\TFHEPk, \TFHESk_1, ..., \TFHESk_N) \gets \TFHESetup(1^\lambda, 1^s, \mathbb{A})$:
		      Takes as input a security parameter $\lambda$, a depth bound on the circuit, and a structure $\mathbb{A} \in \mathbb{S}$.
		      Outputs a public key $\TFHEPk$ and a secret key $\TFHESk_i$ for each party $P_i$.
		\item $\ct \gets \TFHEEncrypt(\TFHEPk, \mu)$: Takes as input a public key and a message $\mu \in \set{0, 1}$ and outputs a ciphertext $\ct$.
		\item $\hat{\ct} \gets \TFHEEval(C, \ct_1, ..., \ct_k)$: Takes as input a circuit $C$ of depth at most $d$ and $k$ ciphertexts $\ct_1, ..., \ct_k$.
		      Outputs a ciphertext $\hat{\ct} = C(\ct_1, ..., \ct_k)$.
		\item $p_i \gets \TFHEPartDec(\ct, \TFHESk_i)$: Takes as input a ciphertext $\ct$ and a secret key $\TFHESk_i$ and outputs a partial decryption $p_i$.
		\item $\hat\mu \gets \TFHEFinDec(B)$: Takes as input a set $B = \set{p_i}_{i \in S}$ for some $S \subseteq [N]$ and deterministically
		      outputs a message $\hat\mu \in \set{0, 1, \bot}$.
	\end{itemize}
	% Let $\mathcal{F}$ be a FHE scheme with key generation algorithm 
\end{definition}

Further we remember the definitions of evaluation correctness and simulation security as outlined in,
\cite{boneh2020single}.

\begin{definition}[Evaluation Correctness \cite{boneh2020single}].
	We have that $\TFHE$ scheme is correct if
	for all $\lambda$, depth bounds $d$, access structure $\mathbb{A}$, circuit $C : \set{0, 1}^k \rightarrow \set{0, 1}$
	of depth at most $d$, $S \in \mathbb{A}$, and $\mu_i \in \set{0, 1}$, we have the following.
	For $(\TFHEPk, \TFHESk_1, ..., \TFHESk_N) \gets \TFHESetup(1^\lambda, 1^d, \mathbb{A})$,
	$\ct_i \gets \TFHEEncrypt(\TFHEPk, \mu_i)$ for $i \in [k]$, $\hat{\ct} \gets \TFHEEval(\TFHEPk, C, \ct_1, ..., \ct_k)$,
	\begin{equation*}
		\Pr\left[\TFHEFinDec(\TFHEPk,
			\set{\TFHEPartDec(\TFHEPk, \hat{\ct}, \TFHESk_i)}_{i \in S}) = C(\mu_1, ..., \mu_k)\right] = 1 - \negl(\lambda).
	\end{equation*}
\end{definition}

\begin{definition}[Semantic Security]
	We have that a $\TFHE$ scheme satisfies semantic security for for all $\lambda$, and depth bound $d$ if the following holds. There is a stateful PPT algorithm
	$\mathcal{S} = (\mathcal{S}_1, \mathcal{S}_2)$ such that for any PPT adversary $\mathcal{A}$,
	the following experiment outputs 1 with negligible probability in $\lambda$:
	\begin{enumerate}
		\item On input $1^\lambda$ and depth $1^d$, the adversary outputs $\mathbb{A} \in \mathbb{S}$
		\item The challenger runs $(\TFHEPk, \TFHESk_1, ..., \TFHESk_N) \gets \TFHESetup(1^\lambda, 1^d, \mathbb{A})$ and provides $\TFHEPk$ to $\advers$.
		\item $\advers$ outputs a set $S \subseteq \set{P_1, ..., P_N}$ such that $\S \notin \mathbb{A}$.
		\item The challenger provides $\set{\TFHESk_i}_{i \in S}$ and $\TFHEEncrypt(\TFHEPk, \mu)$ to $\advers$ where $\mu \overset{\$}{\gets} \set{0, 1}$.
		\item $\advers$ outputs a guess $\mu'$. The experiment outputs 1 if $\mu' = \mu$.
	\end{enumerate}

\end{definition}

\subsection{Data Independent Priority Queue}
In this work, we will use data independent queues as studied in \cite{toft2011secure, mitchell2014data, mazloom2023efficient}.
Data independent data structures are unique as their control flow and memory access do not depend on input data (\cite{mitchell2014data}).

\begin{definition}[Word RAM model \cite{mitchell2014data}]
	In the word RAM model, the RAM has a constant number of public and secret registers and can perform arbitrary operations on a constant number of registers in constant time.
\end{definition}

% TODO: slightly modified definition by me. Check with Mark and come back to it
\begin{definition}[Data Independent Data Structure \cite{mitchell2014data}]
	In the word RAM model, a data independent data structure is a collection of algorithms where
	all the algorithms uses RAM such that the RAM can only set its	control flow based on registers that are public.
\end{definition}

Data independent queues are especially useful as they allow for efficient computation within MPC and FHE as control flow is not dependent
on underlying ciphertexts data. We use a data independent queue as outlined in \cite{mazloom2023efficient}
which allows for
\begin{itemize}
	\item $\PQInsert$: Inserts a tag and value, $(p, x)$ into $\PQ$ according to the tag's priority.
	\item $\PQExtract$: Removes and returns the $(p, y)$ with highest tag priority.
	\item $\PQFront$: Returns the $(p, y)$ with highest tag priority without removing the element.
\end{itemize}
Moreover, we note that the order is stable. I.e.\ the first inserted among equal tagged elements has a higher priority.


\subsection{Resevoir Sampling}
Resevoir sampling is an online algorithm which allows for randomly selecting
$k$ elements from a stream of $n$ elements while using $\tilde{O}(k)$ space.
Algorithm R (\cite{vitter1985random}) is a simple algorithm which relies on a priority queue:
\begin{itemize}
	\item $\ResevInsert(\mu_i, e_i, \texttt{coin}_i)$ where $\mu_i$ is $i$-th item, $e_i$ is independentally sampled randomness,
	and $\texttt{coin}_i$ is a random coin with probability $1/m$ of equaling 1.
	      \begin{itemize}
		      \item If $i \leq k$, insert the item into the queue along with $e_i$ as its tag via $\PQInsert(e_i, \mu_i)$.
		      \item If $i > k$ and $\texttt{coin}_i = 1$, replace the smallest labeled item in the queue with the new item if the coin is 1.
					\item If $i > k$ and $\texttt{coin}_i = 0$, do nothing.
	      \end{itemize}

	\item  $\mu_{a_1}, \mu_{a_2}, ..., \mu_{a_k} \gets \ResevOutput()$ where $a_1, ..., a_k$ are a uniformly random ordered susbset of $[n]$
	\begin{itemize}
		\item Call $\PQExtract$ $k$ times setting $\mu_{a_\ell}$ to the $\ell$-th call to $\PQExtract$ where $\ell \in [k]$.
	\end{itemize}
\end{itemize}



\section{Data Independent Streaming Sampler}
\label{sec:streaming_sampler}
Our construction makes heavy use of a data independent streaming sampler which we will define below.
The streaming sampler relies on a data independent priority queue and in turn makes use of \LS{Cite Shi} protocol for an oblivious priority queue.

\subsection*{
	Encrypted Data Independent Queue
}
In this work, we will data independent queues as studied in \cite{toft2011secure, mitchell2014data, mazloom2023efficient}.
Data independent data structures are unique as their control flow and memory access do not depend on input data (\cite{mitchell2014data}).

They are especially useful as they allow for efficient computation within FHE as control flow is not dependent
on underlying ciphertexts. We use a data independent queue as outlined in \cite{mazloom2023efficient}
which allows for
\begin{itemize}
	\item $\PQInsert$: Inserts a tag and value, $(p, x)$ into $\PQ$ according to the tag's priority.
	\item $\PQExtract$: Removes and returns the $(p, y)$ with highest tag priority.
	\item $\PQFront$: Returns the $(p, y)$ with highest tag priority without removing the element.
\end{itemize}
Moreover, we note that the order is stable. I.e.\ the first inserted among equal tagged elements has a higher priority.

We will use the data independent queue within public key threshold FHE such that we now have an encrypted priority queue, $\EncPQ$
with functionality
\begin{itemize}
	\item $\EncPQInsert$: Inserts a tag and value, $\Enc(p, x)$ into $\PQ$ according to the tag's priority.
	\item $\EncPQExtract$: Removes and returns the $\Enc(p, y)$ with highest tag priority.
	\item $\EncPQFront$: Returns the $\Enc(p, y)$ with highest tag priority without removing the element.
\end{itemize}

We further require that for $\Enc(p, y) \gets \EncPQExtract$ (and $\EncPQFront$) and $x_1, ..., x_n$ drawn from a random distribution,
\begin{align}
	\label{eq:gameEncPQ}
	\Bigl\lvert \Pr[\advers\left(x_1, \dots x_n, \Enc(p_1, x_1), ..., \Enc(p_n, x_n), \Enc(p, y), i\right) = 1] \\
	- \Pr[\advers\left(x_1, \dots x_n, \Enc(p_1, x_1), ..., \Enc(p_n, x_n), \Enc(p, y), j\right) = 1]
	\Bigr\rvert \leq \negl(\lambda) \notag
\end{align}
where $(p_i, x_i)$ and $(p_j, x_j)$ are the $i$th and $j$th submitted message to the priority queue for $i \neq j$.

\begin{lemma}
	Assuming the indistinguishablity of TFHE cipher texts, $\Enc(m_1) \dots \Enc(m_n)$
	where $m_i \neq m_j$ for $i \neq j$ and are known to the adversary, then \cref{eq:gameEncPQ} holds.

	\begin{proof}
		Assume towards contradiction that there exists an adversary $\advers$ which can distinguish between a random
		message to the priority queue and the output of $\EncPQExtract$ (resp. $\EncPQFront$).
		Then, we can construct an adversary $\advers'$ which can distinguish TFHE cipher text, $\ct_1 = \Enc(m_1), \dots, \ct_n = \Enc(m_n)$, as follows:
		\begin{enumerate}
			\item $\advers'$ simulates an encrypted priority queue, $\EncPQ$.
			\item $\advers'$ inserts $x_i = \Enc(\ct_i, r_i)$ into $\EncPQ$ for all $i \in [n]$.
			\item The adversary then calls $\Enc(p, y) \gets \EncPQExtract$ (resp. $\EncPQFront$) and uses $\advers$ to distinguish between $x_1, \dots x_n$.
			\item Output $m_i$ where $\Enc(p, y) = x_i$.
		\end{enumerate}
		Clearly, if the adversary can distinguish the priority queue outcomes, then using $\advers$, he can with non-negligible probability
		distinguish encryptions of $m_1, \dots, m_n$ as the relative ordering of the encryptions is preserved and thus the priority queue repeatably gives the same output.
	\end{proof}
\end{lemma}


\subsection*{Encrypted Streaming Sampler}
A streaming sampler should output a random subset of size $k$ from a stream of $n$ elements with a random ordering.
We can build a streaming sampler from a priority queue as follows:


\begin{algorithm}
	\caption{Encrypted Gated Insert}
	\label{alg:EncIns}
	\begin{algorithmic}
		\Require $\Enc(\text{coin}), \EncPQ, \ct_a$
		\Ensure $\EncPQ$'
		\State $\ct_b \gets \EncPQExtract(\PQ)$
		\State $\ct_{\text{new}} = \Enc(\text{coin}) \cdot \ct_a + (\Enc(\text{coin}) - 1) \cdot \ct_b$
		\State $\EncPQInsert(ct_{\text{new}})$
		\State \Return $\EncPQ$
	\end{algorithmic}
\end{algorithm}

We will use a slightly modified version of a streaming sampler where randomness is submitted alongside the message.
We can then implement the algorithm as follows
\begin{itemize}
	\item $\texttt{Insert}(\ct_i, \Enc(e_i))$ where $\ct_i$ is a cipher text and $\Enc(e_i)$ is encrypted randomness
	      \begin{itemize}
		      \item If the item is the $m$-th item and $m \leq k$, insert the item into the queue along with $e_i$ as its tag via $\EncPQInsert(\Enc(e_i), \ct)$.
		      \item If $m > k$, we will evaluate the PRF (in FHE) to get an encoded random coin which is 1 with probability $1/m$ and 0 otherwise.
		            Then, run \cref{alg:EncIns} which will
		            \begin{itemize}
			            \item replace the smallest labeled item in the queue with the new item if the coin is 1.
			            \item not replace the smallest item in the queue if the coin is 0.
		            \end{itemize}
	      \end{itemize}

	\item At the end of the stream, we output all the items in the priority queue, $\ct_{a_1} ... \ct_{a_k}$ in order
	      by repeatably calling $\EncPQExtract$.

\end{itemize}

We can formalize soundness as a game as follows, for all $\ell \in [k], i, j \in [n]$,
\begin{align}
	\Bigl\lvert
	\Pr[\advers(\ct_1, \dots, \ct_n, e_1, \dots, e_n, \ct_{a_1}, \dots, \ct_{a_k}, \ell, i) = 1] \\
	- \Pr[\advers(\ct_1, \dots, e_1, \dots, \ct_{a_1}, \dots, \ell, j) = 1]
	\Bigr\rvert \leq \negl(\lambda) \notag
\end{align}
In words, the adversary should not be able to guess with any advantage which of the $\ell$-th
outputted cipher text is associated with which inputted cipher text.

\begin{lemma}
	Our construction of a streaming sampler is sound.
	\begin{proof}
		By construction of the streaming sampler, we have that $\Pr[a_\ell = i] = 1/n$ and thus $\Pr[\Dec(\ct_{a_\ell}) = \Dec(\ct_i)] = 1/n$.
		% Now, we need to show that the adversary cannot distinguish between the output of the streaming sampler and a random subset of size $k$.
		...


		% TODO: this should not be too bad
		% Hmmm.... all randomness (add coins) could be input into the protocol, thus its repeatable?
	\end{proof}
\end{lemma}
